Data Exploration

### 2019-02-25 src/stack_test.Rmd
maxent test run

need tidyr package
```{r}
unyears <- as.character(c(1992, 1998)) 
x <- "X"
unyears <- paste0(x, unyears, collapse = NULL) #this adds an X to each year to match with raster naming
unmonths <- c(01, 03)
undepths <- c(10, 86.9294)

unlayer <- crossing(unyears, unmonths, undepths)

for (uny in unyears){
  for (unm in unmonths){
    for (und in undepths){
      year <- unyears[uny]
      month <- unmonths[unm]
      depth <- undepths[und]
    }
  }
}

@@

  }
   # st19980186.9 <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  }
#st19980186.9

>>>>

need tidyr package
```{r}
unyears <- as.character(c("1992", "1998")) 
unyears <- paste0("X", unyears) #this adds an X to each year to match with raster naming
unmonths <- c("01", "03")
undepths <- c("10", "86.9294")

unlayer <- crossing(unyears, unmonths, undepths)
unlayer$stackname <- paste0("st", unlayer$unyears, unlayer$unmonths, unlayer$undepths) #this creates the name of the stack that will be used

@@

#year <- "X1998"
#month <- "01"
#depth <- "86.9294"
tempvar <- "temp"
chlvar <- "chl"
o2var <- "o2"
salvar <- "salinity"
depthvar <- "depth"
surfacevar <- "surface"
naovar <- "nao"
amovar <- "amo"
samplevar <- "sample"
wintervar <- "winter"

for (k in 1:nrow(unlayer)){
    print(unlayer$stackname[k])
    year <- unlayer$unyears[k]
    month <- unlayer$unmonths[k]
    depth <- unlayer$undepths[k]
    for (i in 1:length(rasters)){
    ascyear <- (sapply(strsplit(names(rasters[[i]]), "_"), "[[", 1))
    ascmonth <- (sapply(strsplit(names(rasters[[i]]), "_"), "[[", 2))
    ascdepth <- (sapply(strsplit(names(rasters[[i]]), "_"), "[[", 5))
    ascvar1 <- (sapply(strsplit(names(rasters[[i]]), "_"), "[[", 3))
    ascvar2 <- (sapply(strsplit(names(rasters[[i]]), "_"), "[[", 4))
    ascfile <- rasters[[i]]

    if (ascyear == year & ascmonth == month & ascvar1 == tempvar & ascvar2 == depthvar & ascdepth == depth){
    #print(ascfile)
    temp_depth <- ascfile[[1]]
    names(temp_depth) <- "temp_depth"
  } else if (ascyear == year & ascmonth == month & ascvar1 == chlvar & ascvar2 == surfacevar & ascdepth == depth){
    chl_surface <- ascfile[[1]]
    names(chl_surface) <- "chl_surface"
  } else if (ascyear == year & ascmonth == month & ascvar1 == o2var & ascvar2 == depthvar & ascdepth == depth){
    o2_depth <- ascfile[[1]]
    names(o2_depth) <- "o2_depth"
  } else if (ascyear == year & ascmonth == month & ascvar1 == salvar & ascvar2 == depthvar & ascdepth == depth){
    salinity_depth <- ascfile[[1]]
    names(salinity_depth) <- "salinity_depth"
  } else if (ascyear == year & ascmonth == month & ascvar1 == naovar & ascvar2 == wintervar){
    nao_winter <- ascfile[[1]]
    names(nao_winter) <- "nao_winter"
  } else if (ascyear == year & ascmonth == month  & ascvar1 == naovar & ascvar2 == samplevar){
    nao_sample <- ascfile[[1]]
    names(nao_sample) <- "nao_sample"
  }
}
  }

test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)

#stacklist <- as.list(unlayer$stackname)
#stacklist[2] <- temp_depth

#st19980186.9

#stacktest <- read.csv("../output/bio/stackttest.csv", header = TRUE)
#stacktest$chl <- as.character(stacktest$chl)
#stacktest

```

```{r}
var <- raster(stacktest$chl[1])
var
a <- raster(var)
a
```

#maxent
maxnet throwing errors...
```{r}
janpres <- read.csv("../output/bio/maxenttestjanpr.csv", header = TRUE)
janpres$occ <- 1
janab <- read.csv("../output/bio/maxenttestjanab.csv", header = TRUE)
janab$occ <- 0
prab <- rbind(janpres, janab)
prab$originalscientificname <- "cap" #because species name needs to be the same
pa <- prab$occ
prab <- subset(prab, select = -c(x, y, occ, originalscientificname)) #ok so for maxent in r just need the variables
prab

system.file("java", package="dismo") #finding location to put maxent jar file
system("java -version")
mod1 <- maxent(x = prab, p = pa, path = paste0("../output/maxentout"), args =  c("responsecurves"), save(md, file = "../output/maxentmod"))
pre1 <- predict(mod1, test,  args='outputformat=cloglog')
plot(pre1)
plot(mod1)

```
